### 2014-07-17 ResearchNotes.Rmd
Ran at one point.  It gettting stuck on the sql pull to RTO.  Don't know why it can't find the data.frame.

>>>>

```{r}
summary(KeyForecasts)
summary(KeyLoads)
library(sqldf)

#Join the two parts form the RTO
KeyForecasts$Day<-KeyForecasts$Date
KeyLoads$Day<-KeyLoads$Date

RTO<-sqldf("select KeyForecasts.Day, Forecast, Hour19 from KeyForecasts, KeyLoads where KeyForecasts.Day=KeyLoads.Day;")

GoogleSearch$NextDay<-as.POSIXct(GoogleSearch$Day)+24*60*60

Joint<-sqldf("select RTO.*, GoogleSearch.* from RTO, GoogleSearch where NextDay=Date;")
#fix the forecast again
Joint$Hour19<-as.numeric(as.character(Joint$Hour19))

```
Yes, not a lot of overlap.  Can only do last 30 days with trends for daily.

```{r}
summary(Joint)
summary(lm(Hour19~Forecast+Past_30_days,data=Joint))
```
Looks like it is significant!

```{r}
WO<-lm(Hour19~Forecast,data=Joint)
With<-lm(Hour19~Forecast+Past_30_days,data=Joint)

anova(WO,With)
```

check the change in SE

```{r}
summary(WO)$sigma
summary(With)$sigma

#percent decrease in SE is
(summary(WO)$sigma-summary(With)$sigma)/summary(WO)$sigma
```

Nice! 14% reduction in se.  Proof of concept.
